SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-05 frontrunning/Latex/sections/paper.tex
[frontrunning] Bitcoin cash transaction ordering

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.

>>>>

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols. An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction ID~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully.
